Specific examples

### 2023-05-22 inst/gitbook/02_make.traits.Rmd
man updates

>>>>

## Mapping traits on a tree: `map.traits`

Although `make.traits` is mainly designed for `treats` simulations, i.e. simulating both the trees AND the traits at the same time, it is possible to use an already simulated or estimated tree and generating one or more traits on it using the `map.traits` function. This function takes the trait input as a `"traits"` object (from `make.traits`) and a tree topology with branch length. Note that you can also use `"traits"` objects with multiple or multi-dimensional traits as well as multiple phylogenies (`"multiPhylo"`).

```{r}
## Simulating a random tree with branch length
my_tree <- rtree(20)

## Creating three different traits objects:
## A Brownian Motion
bm_process <- make.traits(process = BM.process)
## An Ornstein-Uhlenbeck process
ou_process <- make.traits(process = OU.process)
## No process (just randomly drawing values from a normal distribution)
no_process <- make.traits(process = no.process)

## Mapping the three traits on the phylogeny
bm_traits <- map.traits(bm_process, my_tree)
ou_traits <- map.traits(ou_process, my_tree)
no_traits <- map.traits(no_process, my_tree)

## Plotting the topology and the different traits
par(mfrow = c(2,2))
plot(my_tree, main = "Base topology")
plot(bm_traits, main = "Mapped BM")
plot(ou_traits, main = "Mapped OU")
plot(no_traits, main = "Mapped normal trait")
```

### 2023-05-22 inst/gitbook/07_specific_examples.Rmd
man updates

@@

```{r}
## A 2D variance covariance matrix
vcv_matrix <- matrix(1, 2, 2)

## A correlated 2D Brownian Motion
correlated_2D_BM <- make.traits(n = 2, process = BM.process,
                      process.args = list(Sigma = vcv_matrix))
```

@@

```{r}
## New correlation
new_vcv <- matrix(c(10,3,3,2),2,2)

## Event changing a trait correlation
correlation.change <- make.events(
    condition    = trait.condition(3, absolute = TRUE),
    target       = "traits",
    modification = traits.update(process.args = list(Sigma = new_vcv)))
```

>>>>

<!-- TODO add a recursive event example where discrete self rate is changed by half everytime you reach 10 living species -->

@@

```{r}
## A 2D variance covariance matrix
cor_matrix <- matrix(1, 2, 2)

## A correlated 2D Brownian Motion
correlated_2D_BM <- make.traits(n = 2, process = BM.process,
                      process.args = list(Sigma = cor_matrix))
```

@@

```{r}
## New correlation
new_cor <- matrix(c(10,3,3,2),2,2)

## Event changing a trait correlation
correlation.change <- make.events(
    condition    = trait.condition(3, absolute = TRUE),
    target       = "traits",
    modification = traits.update(process.args = list(Sigma = new_cor)))
```
